Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex

\subsection{Related work}
\label{sec:related}
%
% Introduce the laplace GNN + shortcomings
One common approach for uncertainty with neural networks is a Laplace GNN approximation \citep{daxbergerLaplace2021}, that takes a trained neural network and linearises it around the optimal weights. The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}. The resultant model is linear with respect to the weights, therefor it is possible to convert it to a Gaussian process (GP) as shown in \citep{immerScalable2021, khan2019approximate}. Yet to obtain uncertainty estimates there is the usual computational scaling  cubic in the number of data points of GPs ($\mathcal{O}(n^3)$). Many approaches  apply crude approximations and yet still obtain good uncertainty estimates.

%% CL section 
%%
%% EWC, SI, VCL -> weight regularization 
EWC \cite{kirkpatrick2017overcoming}
SI \cite{zenke17a}, 
VCL \cite{nguyen-tuongModel2009},

>>>>

\subsection{Related work}
\label{sec:related}
%
% Introduce the laplace GGN + shortcomings
One common approach for uncertainty with neural networks is a Laplace-GGN approximation \citep{daxbergerLaplace2021}, which takes a trained neural network and linearises it around the optimal weights. The resulting linear model can be used to obtain uncertainty estimates and refine the neural network predictions \citep{immerScalable2021}, and is linear with respect to the weights. Therefore, as shown in \citep{immerScalable2021, khan2019approximate}, the linear model can be converted to a Gaussian process (GP), which is then used to obtain the uncertainty estimates.
However, the GP introduces a computational scaling that is cubic in the number of data points ($\mathcal{O}(n^3)$). Many approaches apply crude approximations to alleviate the computational costs, \eg, considering only a subset of the training datas, but are still obtain good uncertainty estimates \citep{immerScalable2021}\todo{other methods?}.

%% CL section 
%%
%% EWC, SI, VCL -> weight regularization

EWC \cite{kirkpatrick2017overcoming}
SI \cite{zenke17a}, 
VCL \cite{nguyen-tuongModel2009},
